---
title: "Design_visualization"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
suppressPackageStartupMessages({ 
library(leaflet) 
library(dplyr)
library(tidyr) 
library(ggplot2)
library(DT) 
  })
```

#load salmon data from the knb

```{r}
data_url <- "https://knb.ecoinformatics.org/knb/d1/mn/v2/object/knb.92020.1"
# data_url <- "https://knb.ecoinformatics.org/knb/d1/mn/v2/object/urn%3Auuid%3Af119a05b-bbe7-4aea-93c6-85434dcb1c5e"
esc <- tryCatch(
    read.csv("data/escapement.csv", stringsAsFactors = FALSE),
    error=function(cond) {
        message(paste("Escapement file does not seem to exist, so get it from the KNB."))
        esc <- read.csv(url(data_url, method = "libcurl"), stringsAsFactors = FALSE)
        return(esc)
    }
)

head(esc)
```

#Prepare the dataset for calculating medians

```{r}
median_esc <- esc %>%
separate(sampleDate, c("Year", "Month", "Day"), sep = "-")

head(median_esc)
```

```{r}
median_esc <- esc %>%
  separate(sampleDate, c("Year", "Month", "Day"), sep = "-") %>% 
  group_by(Species, SASAP.Region, Year, Location) %>% 
  summarize(escapement = sum(DailyCount)) 
head(median_esc)
```

```{r}
median_esc <- esc %>%
  separate(sampleDate, c("Year", "Month", "Day"), sep = "-") %>% 
  group_by(Species, SASAP.Region, Year, Location) %>% 
  summarize(escapement = sum(DailyCount)) %>%
  group_by(Species) %>%
  summarize(median_escapement = median(escapement))

head(median_esc)
```

#Plot the escapement as a bar chart

```{r}
ggplot(median_esc, aes(Species, median_escapement)) + 
  geom_col() +
  #coord_Flip means horizontal bar chart (flips from vertical)
  coord_flip()
```

#Now we work on building a map
We'are starting from daily escapement data again, and finding the unique locations at which escapment was measured

#Find unique location point

make sure to remember to deal with missing values in the location field.


```{r}
locations <- esc %>%
  distinct(Location, Latitude, Longitude) %>% 
  drop_na()
```

```{r}
datatable(locations)
```

#draw the map

```{r}
leaflet(locations) %>% 
  addTiles() %>% 
  addMarkers(~ Longitude, ~ Latitude, popup = ~ Location)

```

# Fix the Map

```{r}
locs <- locations %>% mutate(Longitude = abs(Longitude) * -1)
leaflet(locs) %>% 
  addTiles() %>% 
  addMarkers(~ Longitude, ~ Latitude, popup = ~ Location)
```

```{r}
locs <- locations %>% mutate(Longitude = abs(Longitude) * -1)
leaflet(locs) %>% 
  addTiles() %>% 
  addMarkers(~ Longitude, ~ Latitude, popup = ~ Location)
```

anotgfdkhgdkhgdkhgdhgdkhgdkhgd

